---
title: "Linear Models"
output: github_document
---

```{r}
library(tidyverse)
library(p8105.datasets)
set.seed(1)
```

We will be using `lm` function for linear models
`Glm` for generalized linear models
Outputs are complex and we will use the broom package to clean

## Load and Clean the Airbnb Data

```{r}
data("nyc_airbnb")

nyc_airbnb = 
  nyc_airbnb |> 
  mutate(stars = review_scores_location / 2) |> 
  select(price, stars, borough = neighbourhood_group, neighbourhood, room_type) |> 
  filter(borough != "Staten Island")

```

Let's fit a model

```{r}
fit = 
  nyc_airbnb |> 
  lm(price ~ stars + borough, data = _)

```

How do we look at the results?
These are options that arent used a ton
```{r}

#standard print fit
#fit

summary(fit)
summary(fit)$coef
coef(fit)
#fitted.values(fit)
```


Tidying up the output using broom is important

```{r}
fit |> 
  broom::glance()
```

Tidying up Coefficients - turn into tibble that can then be further reshaped
```{r}
fit |> 
  broom::tidy() |> 
  mutate(term = str_replace(term, "borough", "Borough: ")) |> 
  select(term, estimate, p.value) |> 
  knitr::kable(digits=3)
```

```{r}
fit_2 = 
  nyc_airbnb |> 
  mutate(borough = fct_infreq(borough),
         room_type = fct_infreq(room_type)) |> 
  lm(price ~ stars + borough + room_type, data = _)

fit_2 |> 
  broom::tidy()
```


## Quick look at diagnostics


```{r}
nyc_airbnb |> 
modelr::add_residuals(fit_2) |> 
  ggplot(aes(x = borough, y = resid)) +
  geom_violin()

nyc_airbnb |> 
modelr::add_residuals(fit_2) |> 
  ggplot(aes(x = stars, y = resid)) +
  geom_point()


```

Make sure your modeling does not break the assumptions you started with 


## Hypothesis test for categorical predictor
fit a "null" and "alternative" model
```{r}
fit_2 |> 
  broom::tidy()
#add and remove variable of interest, all else equal and then see if there are signfiicant differences

fit_null = lm(price ~ stars + borough, data = nyc_airbnb)
fit_alternative = lm(price ~ stars + borough + room_type, data = nyc_airbnb)

anova(fit_null, fit_alternative) |> 
  broom::tidy()
```


## Borough-level differences

```{r}
fit_3 =
  nyc_airbnb |> 
  mutate(borough = fct_infreq(borough),
         room_type = fct_infreq(room_type)) |> 
  lm(price ~ stars * borough + room_type * borough, data = _)

fit |> 
  broom::tidy()
```


How to do interactive linear models for each borough to understand borough level differences? Need a function

```{r}
airbnb_lm = function(df) {
  lm(price ~ stars + room_type, data = df)
}

nyc_airbnb |> 
  nest(df = -borough) |> 
  mutate(
    models = map(df, airbnb_lm), 
    results = map(models, broom::tidy)
  ) |> 
  select(borough, results) |> 
  unnest(results) |> 
  select(borough, term, estimate) |> 
  pivot_wider(
    names_from = term,
    values_from = estimate
  ) |> 
  knitr::kable(digits = 2)
```

Making an "anonymous function" shortcut

```{r}
nyc_airbnb |> 
  nest(df = -borough) |> 
  mutate(
    models = map(df, \(df) lm(price ~ stars + room_type, data = df)), 
    results = map(models, broom::tidy)
  ) |> 
  select(borough, results) |> 
  unnest(results) |> 
  select(borough, term, estimate) |> 
  pivot_wider(
    names_from = term,
    values_from = estimate
  ) |> 
  knitr::kable(digits = 2)
```

Look at more complex nesting and binary outcomes: https://p8105.com/linear_models.html#Binary_outcomes



## Homicides in Baltimore
True False test in Resolved - 1 = True, 0 = False
```{r}
baltimore_df = 
  read_csv("Data/homicide-data.csv") |> 
  filter(city == "Baltimore") |> 
  mutate(
    resolved = as.numeric(disposition == "Closed by arrest"),
    victim_age = as.numeric(victim_age)
  ) |> 
  select(resolved, victim_age, victim_race, victim_sex)

baltimore_df
```

fitting a logitic regression

```{r}
fit_logistic = 
  baltimore_df |> 
  glm(
    resolved ~ victim_age + victim_race + victim_sex,
    data = _,
    family = binomial())

```

```{r}
fit_logistic |> 
broom::tidy() |> 
  mutate(OR = exp(estimate)) |> 
  select(term, estimate, OR)
```

