---
title: "Linear Models"
output: github_document
---

```{r}
library(tidyverse)
library(p8105.datasets)
set.seed(1)
```

We will be using `lm` function for linear models
`Glm` for generalized linear models
Outputs are complex and we will use the broom package to clean

## Load and Clean the Airbnb Data

```{r}
data("nyc_airbnb")

nyc_airbnb = 
  nyc_airbnb |> 
  mutate(stars = review_scores_location / 2) |> 
  select(price, stars, borough = neighbourhood_group, neighbourhood, room_type) |> 
  filter(borough != "Staten Island")

```

Let's fit a model

```{r}
fit = 
  nyc_airbnb |> 
  lm(price ~ stars + borough, data = _)

```

How do we look at the results?
These are options that arent used a ton
```{r}

#standard print fit
#fit

summary(fit)
summary(fit)$coef
coef(fit)
#fitted.values(fit)
```


Tidying up the output using broom is important

```{r}
fit |> 
  broom::glance()
```

Tidying up Coefficients - turn into tibble that can then be further reshaped
```{r}
fit |> 
  broom::tidy() |> 
  mutate(term = str_replace(term, "borough", "Borough: ")) |> 
  select(term, estimate, p.value) |> 
  knitr::kable(digits=3)
```

```{r}
fit_2 = 
  nyc_airbnb |> 
  mutate(borough = fct_infreq(borough),
         room_type = fct_infreq(room_type)) |> 
  lm(price ~ stars + borough + room_type, data = _)

fit_2 |> 
  broom::tidy()
```

